Assessing primitives performance\\ on multi-stage execution

### 2018-05-08 paper.tex
add mention of numbered and named primitives

@@

The Slang implementation is written inside the interpreter and has access to all interpreter APIs. Since the same primitive index \cba{Concept to introduce before or rephrase} is used for the primitive with 2 or 3 arguments, the primitive needs to deal with both cases in a way that the common case is efficient. The primitive is now part of the core of the VM, it cannot be easily added or removed as plugin primitives, but it is simpler to read and write. This primitive follows the new specification, the full code is available in Appendix \ref{SlangAppendix}.

>>>>

The primitives can be associated either with a name, either with an index in the Cog VM. The named primitives can be added and modified without the need to recompile the VM.

@@

The Slang implementation is written inside the interpreter and has access to all interpreter APIs. Since the same primitive index is used for the primitive with 2 or 3 arguments, the primitive needs to deal with both cases in a way that the common case is efficient. The primitive is now part of the core of the VM, it cannot be easily added or removed as plugin primitives, but it is simpler to read and write. This primitive follows the new specification, the full code is available in Appendix \ref{SlangAppendix}.
